---
title: "CompareLIs"
author: "Dorothy Bishop"
date: "2023-05-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(here)
require(janitor) #clean up names from external files
```

## Data from fMRI

3 tasks: Word Generation, Auditory Naming and Pyramids and Palm Trees.  
(Also for ftcd on WG and PPT but not AN).
For WG comparison is with rest (contrast 1).
for AN it is with backward speech (contrast 5).   
for PPT it is with line judgement (contrast 5).  

We have data from LI toolbox analysis (already done by Zoe - which includes N voxels - though that seems odd as with bootstrap N voxels is constant? She told me she had hacked into script to get this - maybe this is N voxels at a specific threshold?). For now will read in just the regular LIs for the MCA mask.  
Will eventually want to redo these I think to just check that settings are the same. I also need some indication of confidence interval for these. 

We also now have data from my flip method, which includes t-values as well as means for L and R volumes. 

And I need to read latest fTCD LIs using GAM method. May need to run these for PPT?

So let's start by seeing what data we can read in from existing files. 
Just remembered that I need to use tstat data, so I am going to rerun LI toolbox

NB one missing file for AN and one for PPT. I am just editing the .csv files manually to deal with this for now
 AN is missing subject 085, and PPT is missing subject 068


```{r readdata}
demog <- read_csv(here("Bruckert","_bruckert_summarydat.csv"))
# we'll use this just for demographics, handedness etc

LI_an5 <- read.csv(here("Bruckert","LIComparisons","Toolbox_audnam_t_MCA.csv"))
LI_ppt5 <- read.csv(here("Bruckert","LIComparisons","Toolbox_PPT_t_MCA.csv"))      
LI_wg <- read.csv(here("Bruckert","LIComparisons","Toolbox_WG_t_MCA.csv"))   

LI_an5 <- clean_names(LI_an5)
LI_ppt5 <- clean_names(LI_ppt5)
LI_wg <- clean_names(LI_wg)


flip_an5 <- read.csv(here("Bruckert","LIComparisons","Summaryfliptab_audnam5_MCA.csv"))
flip_ppt5 <- read.csv(here("Bruckert","LIComparisons","Summaryfliptab_ppt5_MCA.csv"))
flip_ppt1 <- read.csv(here("Bruckert","LIComparisons","Summaryfliptab_ppt1_MCA.csv"))
flip_wg <- read.csv(here("Bruckert","LIComparisons","Summaryfliptab_wg_MCA.csv"))

#Now find the GAM values for doppler
dop_wg <- read.csv(here("Bruckert","LIComparisons","DopplerGAM_WG.csv"))
dop_ppt <- read.csv(here("Bruckert","LIComparisons","DopplerGAM_ppt.csv"))




```


I am going to build a new file with just what we need

```{r buildfile}
# start with demog file
keepcols <- c("ID","group_cat", "group_lat","age_at_scan","sex","hand_self_report","hand_EHI")
crosstask <- demog[,keepcols]
crosstask$nonRH <- 1
crosstask$handcolour <- 'red'
crosstask$nonRH[crosstask$hand_self_report=="R"] <- 0
crosstask$handcolour[crosstask$hand_self_report=="R"]  <-'blue'
crosstask$pchcol <- crosstask$group_cat+15
crosstask$pchcol <- as.factor(crosstask$pchcol)
crosstask$subID <- substr(crosstask$ID,1,3)

#would be sensible to make a function to add variables - less likely to make a typo
#but for now...
#now add doppler

crosstask$GAMdopWG <-NA
crosstask$GAMdopWGse <-NA
crosstask$GAMdopPPT<-NA
crosstask$GAMdopPPTse <-NA
crosstask$boot_LI_WG <- NA
crosstask$boot_LI_WGse <- NA
crosstask$boot_LI_PPT5 <- NA
crosstask$boot_LI_PPT5se <- NA
crosstask$boot_LI_AN5 <- NA
crosstask$boot_LI_AN5se <- NA
crosstask$flip_WG <- NA
crosstask$flip_WGse <- NA
crosstask$flip_PPT5 <- NA
crosstask$flip_PPT5se <- NA
crosstask$flip_AN5 <- NA
crosstask$flip_AN5se <- NA
crosstask$flip_PPT1 <- NA
crosstask$flip_PPT1se <- NA

for (i in 1:nrow(crosstask)){
  mysub <- crosstask$subID[i]
  w<-which(substr(dop_wg$Filename,1,3)==mysub )
  if(length(w)>0){
    crosstask$GAMdopWG[i]<-dop_wg$C_LI.est[w]
    crosstask$GAMdopWGse[i]<-dop_wg$C_LIest.se[w]
  }
    w2<-which(substr(dop_ppt$Filename,1,3)==mysub )
  if(length(w2)>0){
    crosstask$GAMdopPPT[i]<-dop_ppt$C_LI.est[w2]
    crosstask$GAMdopPPTse[i]<-dop_ppt$C_LIest.se[w]
  }
}

#now add LI from fmri for all 3 tasks from toolbox
for (i in 1:nrow(crosstask)){
  mysub <- crosstask$subID[i]
  w<-which(substr(LI_wg$id,1,3)==mysub )
  if(length(w)>0){
    crosstask$boot_LI_WG[i]<-LI_wg$li_wm[w]
    crosstask$boot_LI_WGse[i]<-LI_wg$li_sd[w]/sqrt(2000)
  }
    w2<-which(substr(LI_ppt5$id,1,3)==mysub )
  if(length(w2)>0){
    crosstask$boot_LI_PPT5[i]<-LI_ppt$li_wm[w2]
    crosstask$boot_LI_PPT5se[i]<-LI_ppt5$li_sd[w2]/sqrt(2000)
  }
       w3<-which(substr(LI_an5$id,1,3)==mysub )
  if(length(w3)>0){
    crosstask$boot_LI_AN5[i]<-LI_an5$li_wm[w3]
    crosstask$boot_LI_AN5se[i]<-LI_an5$li_sd[w3]/sqrt(2000)
  }
}

#now add flip t values
for (i in 1:nrow(crosstask)){
  mysub <- crosstask$subID[i]
  w<-which(grepl(mysub,flip_wg$file)==TRUE) #finds file ID in that long file string
  if(length(w)>0){
    crosstask$flip_WG[i]<-flip_wg$flip_t[w]
    crosstask$flip_WGse[i]<-flip_wg$sdflipt[w]/sqrt(flip_wg$flipt_DF[w])
  }
  w1<-which(grepl(mysub,flip_ppt5$file)==TRUE) #finds file ID in that long file string
  if(length(w1)>0){
    crosstask$flip_PPT5[i]<-flip_ppt5$flip_t[w1]
    crosstask$flip_PPT5se[i]<-flip_ppt5$sdflipt[w1]/sqrt(flip_ppt5$flipt_DF[w1])
  }
   w2<-which(grepl(mysub,flip_an5$file)==TRUE) #finds file ID in that long file string
  if(length(w2)>0){
    crosstask$flip_AN5[i]<-flip_an5$flip_t[w2]
    crosstask$flip_AN5se[i]<-flip_an5$sdflipt[w2]/sqrt(flip_an5$flipt_DF[w2])
  }
     w3<-which(grepl(mysub,flip_ppt1$file)==TRUE) #finds file ID in that long file string
  if(length(w1)>0){
    crosstask$flip_PPT1[i]<-flip_ppt1$flip_t[w3]
    crosstask$flip_PPT1se[i]<-flip_ppt1$sdflipt[w3]/sqrt(flip_ppt1$flipt_DF[w3])
  }
}



```


```{r function_dofigure,echo=FALSE, messgae = FALSE,warning=FALSE} 
#As we'll make several figures of this kind, we'll make a generic function
dofigure <- function(plotdata,L1,L2,colourcol,pchcol,xlab,ylab,captiontitle1,captiontitle2,xlim,ylim,correlcoef,BlandAltmanlimit,L1se,L2se,showpch){

  myfig <- ggplot(plotdata, aes(x = L1, y = L2,col=colourcol,pch=pchcol)) + 
  geom_point()+
  #theme_bw()+
  xlab(xlab) +  
  ylab(ylab) + 
  xlim(xlim) + ylim(ylim) +
  geom_errorbar(aes(ymin = L2 - L2se, ymax = L2 + L2se),linetype = "solid",size=.3) + 
  geom_errorbarh(aes(xmin = L1 - L1se, xmax = L1 + L1se), linetype = "solid",size=.3) +
  annotate("text",x = 2, y = -1, label = paste('r = ', correlcoef),col='black') +
  geom_hline(yintercept = 0, linetype="solid", alpha = 0.8) + 
  geom_vline(xintercept = 0, linetype= "solid", alpha = 0.8)  + 
  geom_abline(intercept = 0, slope = 1,size=.5,col='grey')+
  geom_abline(intercept = BlandAltmanlimit, slope = 1,linetype="dashed",size=.5,col='grey')+
  geom_abline(intercept = -BlandAltmanlimit, slope = 1,linetype="dashed",size=.5,col='grey')+
  scale_color_discrete(name = captiontitle1)+
    guides(pch=FALSE)
  
return(myfig)
}
```


Now we can look at some comparisons - start within task

```{r exploreplots}
# Correlation between L1 and L2
L1_L2_corr <- cor.test (crosstask$GAMdopWG, crosstask$boot_LI_WG, 
                        method = "spearman", 
                        exact = FALSE)

plotdata=crosstask
L2 = crosstask$GAMdopWG
L1 = crosstask$boot_LI_WG
colourcol = crosstask$handcolour
pchcol = crosstask$pchcol 
 xlab="Doppler GAM LI for WG"
ylab="fMRI bootstrapped LI for WG"
captiontitle1 = "Handed"
captiontitle2 = " "
xlim= c(min(L1),max(L1))
ylim = c(-1,1)
correlcoef <- round(cor.test (L1, L2, method = "spearman",  exact = FALSE)$estimate,3)
 BlandAltmanlimit = 2.5
 L2se = 1.96*crosstask$GAMdopWGse
 L1se = 1.96*crosstask$boot_LI_WGse
showpch = 0

myfig1 <- dofigure(crosstask, L1, L2 ,colourcol ,pchcol, xlab,ylab,captiontitle1,captiontitle2,xlim,ylim ,correlcoef, BlandAltmanlimit, L1se, L2se,showpch)


L2 = crosstask$flip_WG
ylab='fMRI flip t'
ylim = c(min(L2),max(L2))
correlcoef <- round(cor.test (L1, L2, method = "spearman",  exact = FALSE)$estimate,3)
L2se = crosstask$flip_WGse

myfig2 <- dofigure(crosstask, L1, L2 ,colourcol ,pchcol, xlab,ylab,captiontitle1,captiontitle2,xlim,ylim ,correlcoef, BlandAltmanlimit, L1se, L2se,showpch)

L1 = crosstask$GAMdopPPT
L2 = crosstask$boot_LI_PPT5
 xlab="Doppler GAM LI for PPT"
ylab="fMRI bootstrapped LI for PPT5"
xlim= c(min(L1),max(L1))
ylim = c(min(L2),max(L2))
correlcoef <- round(cor.test (L1, L2, method = "spearman",  exact = FALSE)$estimate,3)
 L1se = crosstask$GAMdopPPTse
 L2se = crosstask$boot_LI_PPT5se
myfig3 <- dofigure(crosstask, L1, L2 ,colourcol ,pchcol, xlab,ylab,captiontitle1,captiontitle2,xlim,ylim ,correlcoef, BlandAltmanlimit, L1se, L2se,showpch)

L2 = crosstask$flip_PPT5
ylab='fMRI flip t PPT5'
ylim = c(min(L2),max(L2))
correlcoef <- round(cor.test (L1, L2, method = "spearman",  exact = FALSE)$estimate,3)
L2se = crosstask$flip_PPT5se

myfig4 <- dofigure(crosstask, L1, L2 ,colourcol ,pchcol, xlab,ylab,captiontitle1,captiontitle2,xlim,ylim ,correlcoef, BlandAltmanlimit, L1se, L2se,showpch)

L2 = crosstask$flip_PPT1
ylab='fMRI flip t PPT1'
ylim = c(min(L2),max(L2))
correlcoef <- round(cor.test (L1, L2, method = "spearman",  exact = FALSE)$estimate,3)
L2se = crosstask$flip_PPT1se

myfig5 <- dofigure(crosstask, L1, L2 ,colourcol ,pchcol, xlab,ylab,captiontitle1,captiontitle2,xlim,ylim ,correlcoef, BlandAltmanlimit, L1se, L2se,showpch)

mymat<-cbind(crosstask$GAMdopWG,crosstask$boot_LI_WG,crosstask$flip_WG)
pairs(mymat,c('Doppler','Toolbox','Flip'))
mymat<-cbind(crosstask$GAMdopPPT,crosstask$boot_LI_PPT5,crosstask$flip_PPT5)
pairs(mymat,c('Doppler','Toolbox','Flip'))
mymat<-cbind(crosstask$GAMdopPPT,crosstask$flip_PPT1)
pairs(mymat,c('Doppler','Flip'))
mymat<-cbind(crosstask$boot_LI_AN5,crosstask$flip_AN5)
pairs(mymat,c('Toolbox','Flip'))
mymat<-cbind(crosstask$GAMdopWG,crosstask$GAMdopPPT)
pairs(mymat,c('WG','PPT'))
mymat<-cbind(crosstask$boot_LI_WG,crosstask$boot_LI_PPT5,crosstask$boot_LI_AN5)
pairs(mymat,c('WG','PPT5','AN'))
mymat<-cbind(crosstask$flip_WG,crosstask$flip_PPT5,crosstask$flip_AN5)
pairs(mymat,c('WG','PPT5','AN'))
mymat<-cbind(crosstask$flip_WG,crosstask$flip_PPT1,crosstask$flip_AN5)
pairs(mymat,c('WG','PPT1','AN'))
```

