---
title: "CompareLIs"
author: "Dorothy Bishop"
date: "2023-05-13"
output: html_document
---

18/5/23
updated after adding 95% CI for weighted LI mean
20/5/23
updated to read in the big LI file: li_toolbox_all_tasks_masks_LB.csv
This has 5 and 95% CI
31/5/23
Modified to cope with corrected MCA data, now with binarised mask. NB the raw data files for both toolbox and diff method have been corrected.
7/7/23
To rerun with new outputs from mirror.m and li.m that use 2.5 and 97.5 percentiles

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(here)
require(janitor) #clean up names from external files
require(ggpubr)
require(RVAideMemoire) #for CI for Spearman r
```

## Data from fMRI

3 tasks: Word Generation, Auditory Naming and Pyramids and Palm Trees.  
(Also for ftcd on WG and PPT but not AN).
For WG1 comparison is with rest (contrast 1).
for AN5 it is with backward speech (contrast 5).   
for PP5 it is with line judgement (contrast 5).  
PP1 is semantic judgement vs rest
PP3 is line drawings vs rest

We have latest fTCD LIs using GAM method for WG1 and PP1

For fMRI we have Bruckert data rerun using tstat data and 95% CIs

NB one missing file for AN and one for PPT. 
 AN is missing subject 085, and PPT is missing subject 068
 
Option of including data from toolbox modified to give 6 as top threshold - this is in tbox6summary.csv, and has been done for 3 masks (mca, frontal, parietal) and 2 tasks (WG1 PP1)


```{r readdata}
demog <- read_csv(here("Bruckert","_bruckert_summarydat.csv"))
# we'll use this just for demographics, handedness etc

# Read in data processed with li.m
allLI <- read.csv(here("Bruckert","Data_processed","toolboxsummary.csv"))
allLI <- clean_names(allLI) #from janitor package - names more uniform

#need to get an id that will be the same for all files
#for Lisa's data we can just take the number based on 3 chars of input_image - this is unique to each participant
allLI$id <- substr(allLI$input_image,1,3) #just first 3 chars
idlist <-unique(allLI$id) #complete list of ids - will use later for matching up

#need to code task: this is buried in input_image
allLI$task <- NA
taskID <- c('wordgen_tstat1','ppt_tstat1','ppt_tstat3','ppt_tstat5','audnam_tstat5')
task <- c('WG1','PP1','PP3','PP5','AN5')

for (t in 1:length(task)){
  w<-which(grepl(taskID[t],allLI$input_image)==TRUE)
  allLI$task[w] <-task[t]
}

#now create col for mask
mask <- c('mca','frontal','temporal','parietal','cerebellar')
allLI$mask <- NA
for (m in 1:length(mask)){
  maskname <- mask[m]
  w<-which(grepl(maskname,allLI$inclusive_mask)==TRUE) #find rows with this name
  allLI$mask[w] <-maskname
}

#Now read in mirror files

allmirror <- read.csv(here("Bruckert","Data_processed","mirrorsummary.csv"))
allmirror<-clean_names(allmirror) #this does some odd things to some names but we will fix later!
#find the id in the filename
allmirror$id <-NA #initialise
for (i in 1:length(idlist)){
  id <- idlist[i]
  w<-which(grepl(id,allmirror$filename)==TRUE) #find rows with this id in filename
  allmirror$id[w] <-id
}

for (t in 1:length(task)){
  w<-which(grepl(taskID[t],allmirror$filename)==TRUE)
  allmirror$task[w] <-task[t]
}

#Now find the GAM values for doppler
#We just have 2 tasks: wg1 and pp1
dop_wg1 <- read.csv(here("Bruckert","LIComparisons","DopplerGAM_WG1.csv"))
dop_pp1 <- read.csv(here("Bruckert","LIComparisons","DopplerGAM_pp1.csv"))
dop_wg1$C_lowCI <- dop_wg1$C_LI.est-1.96*dop_wg1$C_LIest.se
dop_wg1$C_hiCI <- dop_wg1$C_LI.est+1.96*dop_wg1$C_LIest.se
dop_pp1$C_lowCI <- dop_pp1$C_LI.est-1.96*dop_pp1$C_LIest.se
dop_pp1$C_hiCI <- dop_pp1$C_LI.est+1.96*dop_pp1$C_LIest.se

#optional : files for tbox6 (max threshold of 6)
tbox6 <- 1
if(tbox6==1){
allLI6 <- read.csv(here("Bruckert","Data_processed","tbox6summary.csv"))
allLI6 <- clean_names(allLI6) #from janitor package - names more uniform

#need to get an id that will be the same for all files
#for Lisa's data we can just take the number based on 3 chars of input_image - this is unique to each participant
allLI6$id <- substr(allLI6$input_image,1,3) #just first 3 chars


#need to code task: this is buried in input_image
allLI6$task <- NA
taskID <- c('wordgen_tstat1','ppt_tstat1')
task <- c('WG1','PP1')

for (t in 1:length(task)){
  w<-which(grepl(taskID[t],allLI6$input_image)==TRUE)
  allLI6$task[w] <-task[t]
}

#now create col for mask
mask <- c('mca','frontal','temporal','parietal','cerebellar')
allLI6$mask <- NA
for (m in 1:length(mask)){
  maskname <- mask[m]
  w<-which(grepl(maskname,allLI6$inclusive_mask)==TRUE) #find rows with this name
  allLI6$mask[w] <-maskname
}
}

```

#scale the doppler values by dividing by 6, and the mirror diff values by dividing by 2.7.
#these values determined by looking at max values
#Aim to bring into range with the LIs with scale from -1 to 1

#We will then make a big dataframe with all the data from doppler and fmri bolted together, with columns for id, method, mask, task,LI, lowCI, highCI

```{r makebigdf}
demog$id <- substr(demog$ID,1,3) #again, we can use first 3 digits of ID to uniquely identify participants

#Long form with methods, tasks, masks all stacked

bigdf <- allmirror[,c('id','meanvol_l','meanvol_r','meandiff','diff_c_ilow','diff_c_ihigh','mask','task')]
names(bigdf)[c(4,5,6)]<-c('mean','lowCI','hiCI') #these are mean and CI for lat index
#scale mirror values by dividing by 2.7 (maximum val for hi CI is 2.689)
bigdf[,4:6]<-bigdf[,4:6]/2.7
bigdf$method <- 'mirror'


#NOW add data from toolbox

#cols for var weighting and clustering just used here as padding for columns with mean L and R activation - will be renamed
addbit<-allLI[,c('id','variance_weighting','clustering','wm_li','wm_low_ci','wm_high_ci','mask','task')]
addbit$method='toolbox'
addbit[,2:3]<-NA
names(addbit)<-names(bigdf)
bigdf<-rbind(bigdf,addbit)

#NOW add data from tbox6
if(tbox6==1){ #optional
#cols for var weighting and clustering just used here as padding for columns with mean L and R activation - will be renamed
addbit<-allLI6[,c('id','variance_weighting','clustering','wm_li','wm_low_ci','wm_high_ci','mask','task')]
addbit$method='tbox6'
addbit[,2:3]<-NA
names(addbit)<-names(bigdf)
bigdf<-rbind(bigdf,addbit)
}
#Now add Doppler - just 2 tasks, equiv to WG1 and PP5 - use NExtreme, nFinal,odd and even for padding

dopbit1 <- dop_wg1[,c('Filename','nExtreme','nFinal','C_LI.est','C_lowCI','C_hiCI','odd','even')]
dopbit1$even <- 'WG1'

dopbit2 <- dop_pp1[,c('Filename','nExtreme','nFinal','C_LI.est','C_lowCI','C_hiCI','odd','even')]
dopbit2$even <- 'PP1'
dopbit <- rbind(dopbit1,dopbit2)

dopbit$method <- 'Doppler'
names(dopbit) <- names(bigdf)
dopbit$id <- substr(dopbit$id,1,3)
dopbit[,2:3]<-NA
dopbit$mask <- 'mca'

#Scale doppler by dividing by 6
w<-which(names(dopbit)=='mean')
dopbit[,w:(w+2)]<-dopbit[,w:(w+2)]/6

#now exclude those who did not do fMRI
w<-which(dopbit$id %in% bigdf$id)
bigdf<- rbind(bigdf,dopbit[w,])


bigdf$hand <- NA
bigdf$lat_group <- NA
for (i in 1:nrow(demog)){
  w<-which(bigdf$id==demog$id[i])
  bigdf$hand[w]<-demog$hand_self_report[i]
  bigdf$lat_group[w]<-demog$group_lat[i]
}

#We include a colour code that can be used later in plotting
bigdf$nonRH <- 1
bigdf$handcolour <- 'blue'
bigdf$nonRH[bigdf$hand=="R"] <- 0
bigdf$handcolour[bigdf$hand=="R"]  <-'red' #Red for right-handed
mypch <- c(19,1,10) #filled circle, open circle, circle with cross -hmm not good with ggplot
bigdf$pchcol <- mypch[bigdf$lat_group]
bigdf$pchcol <- as.factor(bigdf$pchcol)
bigdf$lat_group <- as.factor(bigdf$lat_group)
levels(bigdf$lat_group)<- c('Left','Bilateral','Right')

#NB so far the lat_group is Lisa's original grouping
#Here I will add a new lat_group based on whether this measures CI crossed zero

bigdf$nulatgroup <- 'B'
bigdf$nulatgroup[bigdf$lowCI<0 & bigdf$hiCI<0 ] <- 'R'
bigdf$nulatgroup[bigdf$lowCI>0 & bigdf$hiCI>0 ] <- 'L'

#We also want a new DopLatGroup specific to task, where the task has been given
#Just two tasks: PP1 and WG1. This is just used with LvsR plots so just record this for the mirror method, where
#we have the voxel mean vols
bigdf$Doplat<-NA
for (tt in c('PP1','WG1')){
  myf <- filter(bigdf,bigdf$method=='Doppler',bigdf$task==tt)
  for (n in 1:nrow(myf)){
    w<-intersect(which(bigdf$id==myf$id[n]), which(bigdf$task==tt))
    bigdf$Doplat[w]<-myf$nulatgroup[n]
  }
  
}
write.csv(bigdf,here('Bruckert','Data_processed','bigdf.csv'))
```


Now we can look at some plots - start within task

```{r tryplot}
tryplot <- 0 #this flag can be set to zero so we can skip this step if need be
if (tryplot==1){
 

#method options are "Doppler","mirror","toolbox" 
mymethod <- c('Doppler','mirror','toolbox')
#we select these by specifying 1, 2 or 3
methX <- 1
methY <- 3
methodX <- mymethod[methX]
methodY <- mymethod[methY]
methodlabel <- c('Doppler - rescaled','mirror - rescaled','LI toolbox')
for (thismask in 1:5){
mymask <- mask[thismask]
allplot <- list() #we'll save the plots in a list so we can flexibly reference them later with ggarrange
mycount <-0
tlist <- c(1,4,5) # tasks to include: WG1, PP5, AN5
if(methodX=='Doppler' || methodY =='Doppler'){
  tlist <- c(1,2) #only 2 tasks if Doppler
  mymask <- 'mca'
  } #Doppler only has WG1 and PP1 and mask is always mca
for (t in tlist){
mycount <- mycount+1
mytask <- task[t]

xfile <- filter(bigdf,method==methodX & task==mytask & mask==mymask)
yfile <-  filter(bigdf,method==methodY & task==mytask & mask==mymask)


#Check that rows are equivalent
s<-c(xfile$id,yfile$id)
myn<-table(s)
my2 <- names(which(myn==2))
xfile<-xfile[xfile$id %in% my2,]
yfile <- yfile[yfile$id %in% my2,]
w<-which(names(xfile)=='mean')
names(xfile)[w:(w+2)]<-c('x','xmin','xmax')
names(yfile)[w:(w+2)]<-c('y','ymin','ymax')

forplot<-cbind(xfile,yfile[,w:(w+2)]) #bind x and y columns to make file for plotting

correlcoef <- round(cor.test (forplot$x, forplot$y, method = "spearman",  exact = FALSE)$estimate,3)

corspear <-spearman.ci(forplot$x,forplot$y, nrep = 1000, conf.level = 0.95)
#correlcoef <- paste0('$r_s$ = ',correlcoef,' [',round(corspear$conf.int[1],3),', ',round(corspear$conf.int[2],3),']')
text3 <-paste0('Spearman r: \n',correlcoef,' [',round(corspear$conf.int[1],3),', ',round(corspear$conf.int[2],3),']')

forplot$colgroup <- forplot$lat_group
if(methX>1 && methY>1){forplot$colgroup <- "1"} #no col contrast if only fMRI (needs to be nonnumeric!)

myplot <- ggplot(data = forplot,aes(x = x,y = y)) + 
  geom_point(aes(col=colgroup),size=1.5)+
  geom_errorbar(aes(ymin = ymin,ymax = ymax,col=colgroup)) + 
  geom_errorbarh(aes(xmin = xmin,xmax = xmax,col=colgroup))+
  geom_hline(yintercept = 0, linetype="solid",col='grey') + 
  geom_vline(xintercept = 0, linetype= "solid", col='grey')  + 
  xlab(methodlabel[methX])+
  ylab(methodlabel[methY])+
  xlim(-1,1)+
  ylim(-1,1)+
  ggtitle(paste0(mymask,": ",mytask))+
  annotate("text",x = -.5, y = .9, label = text3,col='black',size=3)+
   theme(legend.position = "none")

mylegend=FALSE
if(methX==1 || methY==1){
myplot <- myplot +
  guides(col=guide_legend(title='Laterality category: fTCD WG'))
  mylegend=TRUE
}

if(methX>1 && methY>1){
myplot <- myplot +
   scale_color_manual(values = "blue") #just use blue points if plotting only fMRI
}



 
allplot[[mycount]] = myplot
}
if(length(allplot)==3){
myallplot <- ggarrange(allplot[[1]],allplot[[3]],allplot[[2]],ncol=3,nrow=1,common.legend=mylegend)
savename<-paste0(methodX,'_',methodY,'_3tasks_',mymask,'.jpg')
}
if(length(allplot)==2){
myallplot <- ggarrange(allplot[[1]],allplot[[2]],ncol=2,nrow=1,common.legend=mylegend)
savename<-paste0(methodX,'_',methodY,'_2tasks_',mymask,'.jpg')
}
ggsave(here('Bruckert','Plots',savename),myallplot,width=8,height=3,dpi=300)
}

}

```


```{r LRplot}
LRplot <- 0
if(LRplot==1){
#column with 'diff'
masktitle <- c('MCA','Frontal','Temporal','Parietal','Cerebellar')
tasktitle <- c('Word Generation','Semantic vs rest','Line vs rest','Semantic vs Line','Auditory Naming')
methodX <- 'mirror'
mycount <-0
allplot <- list()
for (thismask in 2:5){
mymask <- mask[thismask]


for (t in c(1,2,5)){ #WG1, PP1, AN5
mycount <- mycount+1
mytask <- task[t]
forplot <- filter(bigdf,method==methodX & task==mytask & mask==mymask)

names(forplot)[2:3]<-c('Left','Right')


#correlcoef <- round(cor.test (forplot$Left, forplot$Right, method = "spearman",  exact = FALSE)$estimate,3) #not used
#censor values at 3
mycensor <- 3
forplot$Left[forplot$Left< (-mycensor)]<- (-mycensor)
forplot$Right[forplot$Right< (-mycensor)]<- (-mycensor)
 forplot$Left[forplot$Left>mycensor]<- mycensor
 forplot$Right[forplot$Right>mycensor]<- mycensor
myplot <- ggplot(data = forplot,aes(x = Right,y = Left)) + 
  geom_point(aes(col=Doplat),size=1.5)+
  geom_hline(yintercept = 0, linetype="solid",col='grey') + 
  geom_vline(xintercept = 0, linetype= "solid", col='grey')  + 
  geom_abline(intercept=0,slope=1,linetype= "dotted", col='black')+
  geom_hline(yintercept = mean(forplot$Left[forplot$Doplat=='L']),col='blue',linetype= "dashed")+
  geom_vline(xintercept = mean(forplot$Right[forplot$Doplat=='L']),col='blue',linetype= "dashed")+
  xlab("Activation R")+
  ylab("Activation L")+
   xlim(-mycensor,mycensor)+
   ylim(-mycensor,mycensor)+
  ggtitle(paste0(masktitle[thismask],":\n",tasktitle[t]))+
  scale_color_manual(values=c( "purple","blue","red"))+
  guides(col=guide_legend(title='Laterality category: fTCD'))


 
allplot[[mycount]] = myplot
}
}
myallplot <- ggarrange(allplot[[1]],allplot[[2]],allplot[[3]],allplot[[4]],allplot[[5]],allplot[[6]],allplot[[7]],allplot[[8]],allplot[[9]],allplot[[10]],allplot[[11]],allplot[[12]],ncol=3,nrow=4,common.legend=TRUE)
savename<-paste0('LR_3tasks_4mask.png')
ggsave(here('Bruckert','Plots',savename),myallplot,width=6,height=10,dpi=300)

}
```

```{r plot5regions}
plot5 <-0
if(plot5==1){
#method options are "Doppler","mirror","toolbox" - now with mirrorLI which is LI from mirror data
mymethod <- c('Doppler','mirror','toolbox')
tlist <- c('WG1','PP1','PP5')
longlist <- c('Word Generation', 'Semantic Match','Sem Match - Baseline')#
for (t in 1:length(tlist)){ #new plot started with new task
mytask <- tlist[t]
longtask <- longlist[t]
allplot <- list() #clear list
mycount <-0
methX <- 1
for (methY in 2:3){ #methods 2 and 3 will be compared side by side
methodX <- mymethod[methX]
methodY <- mymethod[methY]
methodlabel <- c('fTCD GAM - rescaled','fMRI: Subtracted - rescaled','fMRI: LI toolbox','LI from mirror')

mytaskx <- mytask
if(mytaskx=='PP5' && methX ==1){mytaskx <- 'PP1'}

for (thismask in 1:5){
mymask <- mask[thismask]
mytitle <- paste0(str_to_title(mymask),": ",longtask)
if(thismask==1){
  mytitle <- paste0(str_to_upper(mymask),": ",longtask)
}

mycount <- mycount+1 #used to count the plots

xfile <- filter(bigdf,method==methodX & task==mytaskx & mask=='mca') #doppler only has mca equiv and only has pp1 and wg1
yfile <-  filter(bigdf,method==methodY & task==mytask & mask==mymask)



#Check that rows are equivalent
s<-c(xfile$id,yfile$id)
myn<-table(s)
my2 <- names(which(myn==2))
xfile<-xfile[xfile$id %in% my2,]
yfile <- yfile[yfile$id %in% my2,]
w<-which(names(xfile)=='mean')
names(xfile)[w:(w+2)]<-c('x','xmin','xmax')
names(yfile)[w:(w+2)]<-c('y','ymin','ymax')
pbilat <- round(100*length(which(yfile$nulatgroup=='B'))/nrow(yfile),0) #% bilat
forplot<-cbind(xfile,yfile[,w:(w+2)])

corspear <-spearman.ci(forplot$x,forplot$y, nrep = 1000, conf.level = 0.95)
rs <- round(corspear$estimate,3)
ci1<-round(corspear$conf.int[1],3)
ci2<-round(corspear$conf.int[2],3)
cortext <- paste0('r[s] = ',rs,'\n[',ci1,', ', ci2,']')

#add some text re % bilateral


myplot <- ggplot(data = forplot,aes(x = x,y = y)) + 
  geom_point(aes(col='black'),size=1.5)+
  geom_errorbar(aes(ymin = ymin,ymax = ymax,col='black')) + 
  geom_errorbarh(aes(xmin = xmin,xmax = xmax,col='black'))+
  geom_hline(yintercept = 0, linetype="solid",col='grey') + 
  geom_vline(xintercept = 0, linetype= "solid", col='grey')  + 
  xlab(methodlabel[methX])+
  ylab(methodlabel[methY])+
  xlim(-1,1)+
  ylim(-1,1)+
  ggtitle(mytitle)+
  annotate("text",x = -.5, y = .9, label = cortext,col='black')+
  annotate("text",x = 0.65, y = -.85, label = paste0(pbilat,'% bilateral'),col='black')+
  guides(col=guide_legend(title='Laterality category: fTCD WG'))

allplot[[mycount]] = myplot
}
}

myallplot <- ggarrange(allplot[[1]],allplot[[6]],allplot[[2]],allplot[[7]],allplot[[3]],
                       allplot[[8]],allplot[[4]],allplot[[9]],allplot[[5]],allplot[[10]],nrow=5,ncol=2,common.legend=TRUE)
savename<-paste0('Doppler_fmri2meth_5masks_',mytask,'.jpg')

ggsave(here('Plots',savename),myallplot,width=8,height=15,dpi=300)

#additional plots for powerpoint
myplot1 <- ggarrange(allplot[[1]],allplot[[6]],nrow=1,ncol=2,common.legend=TRUE)
savename<-paste0('Doppler_fmri2meth_MCA_',mytask,'.jpg')

ggsave(here('Plots',savename),myplot1,width=6,height=4,dpi=300)

#additional plots for powerpoint
myplot2 <- ggarrange(allplot[[2]],allplot[[7]],allplot[[3]],allplot[[8]],nrow=2,ncol=2,common.legend=TRUE)
savename<-paste0('Doppler_fmri2meth_fronttemp_',mytask,'.jpg')

ggsave(here('Plots',savename),myplot2,width=6,height=6,dpi=300)

myplot3 <- ggarrange(allplot[[4]],allplot[[9]],allplot[[5]],allplot[[10]],nrow=2,ncol=2,common.legend=TRUE)
savename<-paste0('Doppler_fmri2meth_parcereb_',mytask,'.jpg')

ggsave(here('Bruckert','Plots',savename),myplot3,width=6,height=6,dpi=300)
}

}
```

now look at toolbox vs tbox6


```{r tryplot2}
tryplot2 <- 0 #this flag can be set to zero so we can skip this step if need be
if (tryplot2==1){
 
mymethod <- c('tbox6','toolbox')

methX <- 1
methY <- 2
methodX <- mymethod[methX]
methodY <- mymethod[methY]
methodlabel <- c('Toolbox_thresh6','Toolbox-threshmax')
mycount <-0
allplot <- list() #we'll save the plots in a list so we can flexibly reference them later with ggarrange
tlist <- c(1,2) # tasks to include: WG1, PP1
for (thismask in c(1,2,4)){
mymask <- mask[thismask]

for (t in tlist){
mycount <- mycount+1
mytask <- task[t]

xfile <- filter(bigdf,method==methodX & task==mytask & mask==mymask)
yfile <-  filter(bigdf,method==methodY & task==mytask & mask==mymask)

w<-which(names(xfile)=='mean')
names(xfile)[w:(w+2)]<-c('x','xmin','xmax')
names(yfile)[w:(w+2)]<-c('y','ymin','ymax')
forplot<-cbind(xfile,yfile[,w:(w+2)]) #bind x and y columns to make file for plotting


correlcoef <- round(cor.test (forplot$x, forplot$y, method = "spearman",  exact = FALSE)$estimate,3)

corspear <-spearman.ci(forplot$x,forplot$y, nrep = 1000, conf.level = 0.95)
#correlcoef <- paste0('$r_s$ = ',correlcoef,' [',round(corspear$conf.int[1],3),', ',round(corspear$conf.int[2],3),']')
text3 <-paste0('Spearman r: \n',correlcoef,' [',round(corspear$conf.int[1],3),', ',round(corspear$conf.int[2],3),']')

text2 <- paste0('mean X = ',round(mean(forplot$x),2),'; \nmean Y = ',round(mean(forplot$y),2))
myplot <- ggplot(data = forplot,aes(x = x,y = y)) + 
  geom_point()+
  #geom_errorbar(aes(ymin = ymin,ymax = ymax)) + 
  #geom_errorbarh(aes(xmin = xmin,xmax = xmax))+
  xlab(methodlabel[methX])+
  ylab(methodlabel[methY])+
  xlim(-1,1)+
  ylim(-1,1)+
  ggtitle(paste0(mymask,": ",mytask))+
  geom_hline(yintercept = 0, linetype="solid",col='grey') + 
  geom_vline(xintercept = 0, linetype= "solid", col='grey')  + 
  geom_abline(slope=1,intercept=0)+
  annotate("text",x = -.5, y = .9, label = text3,col='black',size=3)+
    annotate("text",x = -.5, y = .65, label = text2,col='black',size=3)+
   theme(legend.position = "none")



allplot[[mycount]] = myplot
}
}

myallplot <- ggarrange(allplot[[1]],allplot[[2]],allplot[[3]],allplot[[4]],allplot[[5]],allplot[[6]],ncol=2,nrow=3,common.legend=mylegend)
savename<-paste0(methodX,'_',methodY,'_2tasks_3masks.jpg')

ggsave(here('Bruckert','Plots',savename),myallplot,width=8,height=12,dpi=300)

}

```

Do correlations between regions and/or tasks look higher for the tbox6 than original toolbox?
Need to reshape data!

```{r correls}
require(corrplot)
forcorrel<-bigdf[bigdf$method %in% c('toolbox','tbox6'),]
forcorrel<-select(forcorrel,id,method, mask,task,mean)
forcorrel <-filter(forcorrel,task %in% c('WG1','PP1'))
forcorrel <- filter(forcorrel, mask %in% c('mca','frontal','parietal'))

lat.wide1 <- spread(forcorrel,key=c('method'),value='mean')

allids <- unique(bigdf$id)
cordata <- data.frame(matrix(NA,nrow=length(unique(lat.wide1$id)),ncol=13))
names(cordata)[1]<-'id'
masks<-c('mca','frontal','parietal')
tasks <- c('WG1','PP1')
meths <- unique(forcorrel$method)
for (i in 1:nrow(cordata)){
thiscol <-1
for (n in 1:2){
    for (t in 1:2){
     for (m in 1:3){

    thiscol<-thiscol+1

      thisdat = filter(forcorrel,id==allids[i],method==meths[n],task==tasks[t],mask==masks[m])
      cordata[i,1]<-allids[i]
      if(nrow(thisdat)>0){
      cordata[i,thiscol]<-thisdat$mean
      }
      if(i==1){
        names(cordata)[thiscol]<-paste0(meths[n],masks[m],tasks[t])
       }
  }
}
}
}

#rquery.cormat(cordata[,2:])
round(cor(cordata[,2:7],use='complete.obs'),3)
round(cor(cordata[,8:13],use='complete.obs'),3)
```

