---
title: "CompareLIs"
author: "Dorothy Bishop"
date: "2023-05-13"
output: html_document
---

18/5/23
updated after adding 95% CI for weighted LI mean
20/5/23
updated to read in the big LI file: li_toolbox_all_tasks_masks_LB.csv
This has 5 and 95% CI
31/5/23
Modified to cope with corrected MCA data, now with binarised mask. NB the raw data files for both toolbox and diff method have been corrected.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(here)
require(janitor) #clean up names from external files
require(ggpubr)
require(RVAideMemoire) #for CI for Spearman r
```

## Data from fMRI

3 tasks: Word Generation, Auditory Naming and Pyramids and Palm Trees.  
(Also for ftcd on WG and PPT but not AN).
For WG1 comparison is with rest (contrast 1).
for AN5 it is with backward speech (contrast 5).   
for PP5 it is with line judgement (contrast 5).  
PP1 is semantic judgement vs rest
PP3 is line drawings vs rest

We have data from LI toolbox analysis (already done by Zoe - which includes N voxels - though that seems odd as with bootstrap N voxels is constant? She told me she had hacked into script to get this - maybe this is N voxels at a specific threshold?). For now will read in just the regular LIs. 

We also now have data from my flip method, which includes differences and 95% CI for differences, plus t-values as well as means for L and R volumes. 

Also have latest fTCD LIs using GAM method for WG1 and PP1

All LI and flip rerun using tstat data

NB one missing file for AN and one for PPT. 
 AN is missing subject 085, and PPT is missing subject 068


```{r readdata}
demog <- read_csv(here("Bruckert","_bruckert_summarydat.csv"))
# we'll use this just for demographics, handedness etc
allLI <- read.csv(here("Bruckert","LIComparisons","li_toolbox_all_tasks_masks_LB.csv"))
allLI <- clean_names(allLI)
allLI$id <- substr(allLI$id,1,3) #just first 3 chars


#find task buried in input_image
allLI$task <- NA
taskID <- c('wordgen_tstat1','ppt_tstat1','ppt_tstat3','ppt_tstat5','audnam_tstat5')
task <- c('WG1','PP1','PP3','PP5','AN5')

for (t in 1:length(task)){
  w<-which(grepl(taskID[t],allLI$input_image)==TRUE)
  allLI$task[w] <-task[t]
}

mask <- c('mca','frontal','temporal','parietal','cerebellar')
allLI$mask <- NA
for (m in 1:length(mask)){
  maskname <- paste0('LI-',mask[m],'-mask.img,1')
  if(m==1){
      maskname <- paste0('LI-',mask[m],'-mask.nii')
  }
   w<-which(grepl(maskname,allLI$inclusive_mask)==TRUE)
  allLI$mask[w] <-mask[m]
}



#flip files with 5% selected (can substitute another file if need be)
flip_all <- read.csv(here("Bruckert","LIComparisons","Summaryfliptab_all_LI_1000_5.csv"))
flip_all<-clean_names(flip_all)
w<-which(flip_all$mask=='MCA')
flip_all$mask[w]<-'mca'
flip_all$id<-substr(flip_all$id,1,3)


#Now find the GAM values for doppler
dop_wg1 <- read.csv(here("Bruckert","LIComparisons","DopplerGAM_WG1.csv"))
dop_pp1 <- read.csv(here("Bruckert","LIComparisons","DopplerGAM_pp1.csv"))
dop_wg1$C_lowCI <- dop_wg1$C_LI.est-1.96*dop_wg1$C_LIest.se
dop_wg1$C_hiCI <- dop_wg1$C_LI.est+1.96*dop_wg1$C_LIest.se
dop_pp1$C_lowCI <- dop_pp1$C_LI.est-1.96*dop_pp1$C_LIest.se
dop_pp1$C_hiCI <- dop_pp1$C_LI.est+1.96*dop_pp1$C_LIest.se

```

#scale the doppler values by dividing by 6, and the flip diff values by dividing by 2.7.
#these values determined by looking at max values
#Aim to bring into range with the LIs - but not otherwise equiv


```{r makebigdf}
demog$id <- substr(demog$ID,1,3)

#Long form with methods, tasks, masks all stacked

bigdf <- flip_all[,c('id','meanvol_l','meanvol_r','meandiff','diff_low_ci','diff_hi_ci','li','li_p5','li_p95','mask','task')]
names(bigdf)[c(4,5,6)]<-c('mean','lowCI','hiCI')
#scale flip values by dividing by 2.7 (maximum val for hi CI is 2.657)
bigdf[,4:6]<-bigdf[,4:6]/2.7
bigdf$method <- 'flip'

bigdf2<-bigdf #make a copy which will hold the LI from the flip method
bigdf2$method <- 'flipLI'

#just delete unwanted cols for each and then bolt together
w<-which(names(bigdf)=='li')
bigdf<-bigdf[,-(w:(w+2))]

x<-which(names(bigdf2)=='mean')
bigdf2<-bigdf2[,-(x:(x+2))]
names(bigdf2)[x:(x+2)]<-names(bigdf)[x:(x+2)]

bigdf<-rbind(bigdf,bigdf2)

#NOW add data from toolbox


#cols for var weighting and clustering just used here as padding for correct N cols
addbit<-allLI[,c('id','variance_weighting','clustering','li_wm','li_p5','li_p95','mask','task')]
addbit$method='toolbox'
addbit[,2:3]<-NA
names(addbit)<-names(bigdf)
bigdf<-rbind(bigdf,addbit)


#Now add Doppler - just 2 tasks, equiv to WG1 and PP5 - use NExtreme, nFinal,odd and even for padding

dopbit1 <- dop_wg1[,c('Filename','nExtreme','nFinal','C_LI.est','C_lowCI','C_hiCI','odd','even')]
dopbit1$even <- 'WG1'

dopbit2 <- dop_pp1[,c('Filename','nExtreme','nFinal','C_LI.est','C_lowCI','C_hiCI','odd','even')]
dopbit2$even <- 'PP1'
dopbit <- rbind(dopbit1,dopbit2)

dopbit$method <- 'Doppler'
names(dopbit) <- names(bigdf)
dopbit$id <- substr(dopbit$id,1,3)
dopbit[,2:3]<-NA
dopbit$mask <- 'mca'

#Scale doppler by dividing by 6
w<-which(names(dopbit)=='mean')
dopbit[,w:(w+2)]<-dopbit[,w:(w+2)]/6

#now exclude those who did not do fMRI
w<-which(dopbit$id %in% bigdf$id)
bigdf<- rbind(bigdf,dopbit[w,])


bigdf$hand <- NA
bigdf$lat_group <- NA
for (i in 1:nrow(demog)){
  w<-which(bigdf$id==demog$id[i])
  bigdf$hand[w]<-demog$hand_self_report[i]
  bigdf$lat_group[w]<-demog$group_lat[i]
}

bigdf$nonRH <- 1
bigdf$handcolour <- 'red'
bigdf$nonRH[bigdf$hand=="R"] <- 0
bigdf$handcolour[bigdf$hand=="R"]  <-'blue'
mypch <- c(19,1,10) #filled circle, open circle, circle with cross -hmm not good with ggplot
bigdf$pchcol <- mypch[bigdf$lat_group]
bigdf$pchcol <- as.factor(bigdf$pchcol)
bigdf$lat_group <- as.factor(bigdf$lat_group)
levels(bigdf$lat_group)<- c('Left','Bilateral','Right')

#NB so far the lat_group is Lisa's original grouping
#Here I will add a new lat_group based on whether this measures CI crossed zero

bigdf$nulatgroup <- 'B'
bigdf$nulatgroup[bigdf$lowCI<0 & bigdf$hiCI<0 ] <- 'R'
bigdf$nulatgroup[bigdf$lowCI>0 & bigdf$hiCI>0 ] <- 'L'

#We also want a new DopLatGroup specific to task, where the task has been given
#Just two tasks: PP1 and WG1. This is just used with LvsR plots so just record this for the flip method, where
#we have the voxel mean vols
bigdf$Doplat<-NA
for (tt in c('PP1','WG1')){
  myf <- filter(bigdf,bigdf$method=='Doppler',bigdf$task==tt)
  for (n in 1:nrow(myf)){
    w<-intersect(which(bigdf$id==myf$id[n]), which(bigdf$task==tt))
    bigdf$Doplat[w]<-myf$nulatgroup[n]
  }
  
}

```


Now we can look at some comparisons - start within task

```{r tryplot}
tryplot <- 0
if (tryplot==1){
  

#method options are "Doppler","flip","toolbox" - now with flipLI which is LI from flip data
mymethod <- c('Doppler','flip','toolbox','flipLI')
meth1 <- 1
meth2 <- 4
method1 <- mymethod[meth1]
method2 <- mymethod[meth2]
methodlabel <- c('Doppler - rescaled','Flip - rescaled','LI toolbox','LI from flip')
for (thismask in 1:5){
mymask <- mask[thismask]
allplot <- list()
mycount <-0
tlist <- c(1,4,5)#WG1, PP5, AN5
if(method1=='Doppler' || method2 =='Doppler'){
  tlist <- c(1,2)
  mymask <- 'mca'
  } #Doppler only has WG1 and PP1 and is equiv mca
for (t in tlist){
mycount <- mycount+1
mytask <- task[t]

xfile <- filter(bigdf,method==method1 & task==mytask & mask==mymask)
yfile <-  filter(bigdf,method==method2 & task==mytask & mask==mymask)


#Check that rows are equivalent
s<-c(xfile$id,yfile$id)
myn<-table(s)
my2 <- names(which(myn==2))
xfile<-xfile[xfile$id %in% my2,]
yfile <- yfile[yfile$id %in% my2,]
w<-which(names(xfile)=='mean')
names(xfile)[w:(w+2)]<-c('x','xmin','xmax')
names(yfile)[w:(w+2)]<-c('y','ymin','ymax')

forplot<-cbind(xfile,yfile[,w:(w+2)])

correlcoef <- round(cor.test (forplot$x, forplot$y, method = "spearman",  exact = FALSE)$estimate,3)

corspear <-spearman.ci(forplot$x,forplot$y, nrep = 1000, conf.level = 0.95)
correlcoef <- paste0('r',)


myplot <- ggplot(data = forplot,aes(x = x,y = y)) + 
  geom_point(aes(col=lat_group),size=1.5)+
  geom_errorbar(aes(ymin = ymin,ymax = ymax,col=lat_group)) + 
  geom_errorbarh(aes(xmin = xmin,xmax = xmax,col=lat_group))+
  geom_hline(yintercept = 0, linetype="solid",col='grey') + 
  geom_vline(xintercept = 0, linetype= "solid", col='grey')  + 
  xlab(methodlabel[meth1])+
  ylab(methodlabel[meth2])+
  xlim(-1,1)+
  ylim(-1,1)+
  ggtitle(paste0(mymask,": ",mytask))+
  annotate("text",x = -.5, y = .9, label = paste('r = ', correlcoef),col='black')+
  guides(col=guide_legend(title='Laterality category: fTCD WG'))


 
allplot[[mycount]] = myplot
}
if(length(allplot)==3){
myallplot <- ggarrange(allplot[[1]],allplot[[3]],allplot[[2]],ncol=3,nrow=1,common.legend=TRUE)
savename<-paste0(method1,'_',method2,'_3tasks_',mymask,'.jpg')
}
if(length(allplot)==2){
myallplot <- ggarrange(allplot[[1]],allplot[[2]],ncol=2,nrow=1,common.legend=TRUE)
savename<-paste0(method1,'_',method2,'_2tasks_',mymask,'.jpg')
}
ggsave(here('Plots',savename),myallplot,width=8,height=4,dpi=300)
}

}

```


```{r LRplot}
LRplot <- 1
if(LRplot==1){
#column with 'diff'
masktitle <- c('MCA','Frontal','Temporal','Parietal','Cerebellar')
tasktitle <- c('Word Generation','Semantic vs rest','Line vs rest','Semantic vs Line','Auditory Naming')
method1 <- 'flip'
for (thismask in 1:5){
mymask <- mask[thismask]
allplot <- list()
mycount <-0
for (t in c(1,2)){ #WG1, PP5, AN5
mycount <- mycount+1
mytask <- task[t]
forplot <- filter(bigdf,method==method1 & task==mytask & mask==mymask)
w<-which(is.na(forplot$Doplat)) #find and remove rows with no Doppler lat
forplot <- forplot[-w,]
names(forplot)[2:3]<-c('Left','Right')


correlcoef <- round(cor.test (forplot$Left, forplot$Right, method = "spearman",  exact = FALSE)$estimate,3)
#censor values at 3
mycensor <- 3
forplot$Left[forplot$Left< (-mycensor)]<- (-mycensor)
forplot$Right[forplot$Right< (-mycensor)]<- (-mycensor)
 forplot$Left[forplot$Left>mycensor]<- mycensor
 forplot$Right[forplot$Right>mycensor]<- mycensor
myplot <- ggplot(data = forplot,aes(x = Right,y = Left)) + 
  geom_point(aes(col=Doplat),size=2)+
  geom_hline(yintercept = 0, linetype="solid",col='grey') + 
  geom_vline(xintercept = 0, linetype= "solid", col='grey')  + 
  geom_abline(intercept=0,slope=1,linetype= "dotted", col='black')+
  geom_hline(yintercept = mean(forplot$Left),col='brown',linetype= "dashed")+
  geom_vline(xintercept = mean(forplot$Right),col='brown',linetype= "dashed")+
  xlab("Activation R")+
  ylab("Activation L")+
   xlim(-mycensor,mycensor)+
   ylim(-mycensor,mycensor)+
  ggtitle(paste0(masktitle[thismask],":\n",tasktitle[t]))+
  guides(col=guide_legend(title='Laterality category: fTCD'))


 
allplot[[mycount]] = myplot
}
myallplot <- ggarrange(allplot[[1]],allplot[[2]],ncol=2,nrow=1,common.legend=TRUE)
savename<-paste0('LR_3tasks_',mymask,'.jpg')
ggsave(here('Plots',savename),myallplot,width=8,height=4,dpi=300)
}
}
```

```{r plot5regions}

#method options are "Doppler","flip","toolbox" - now with flipLI which is LI from flip data
mymethod <- c('Doppler','flip','toolbox','flipLI')
tlist <- c('WG1','PP1','PP5')
longlist <- c('Word Generation', 'Semantic Match','Sem Match - Baseline')#
for (t in 1:length(tlist)){ #new plot started with new task
mytask <- tlist[t]
longtask <- longlist[t]
allplot <- list() #clear list
mycount <-0
meth1 <- 1
for (meth2 in 2:3){ #methods 2 and 3 will be compared side by side
method1 <- mymethod[meth1]
method2 <- mymethod[meth2]
methodlabel <- c('fTCD GAM - rescaled','fMRI: Subtracted - rescaled','fMRI: LI toolbox','LI from flip')

mytaskx <- mytask
if(mytaskx=='PP5' && meth1 ==1){mytaskx <- 'PP1'}

for (thismask in 1:5){
mymask <- mask[thismask]
mytitle <- paste0(str_to_title(mymask),": ",longtask)
if(thismask==1){
  mytitle <- paste0(str_to_upper(mymask),": ",longtask)
}

mycount <- mycount+1 #used to count the plots

xfile <- filter(bigdf,method==method1 & task==mytaskx & mask=='mca') #doppler only has mca equiv and only has pp1 and wg1
yfile <-  filter(bigdf,method==method2 & task==mytask & mask==mymask)



#Check that rows are equivalent
s<-c(xfile$id,yfile$id)
myn<-table(s)
my2 <- names(which(myn==2))
xfile<-xfile[xfile$id %in% my2,]
yfile <- yfile[yfile$id %in% my2,]
w<-which(names(xfile)=='mean')
names(xfile)[w:(w+2)]<-c('x','xmin','xmax')
names(yfile)[w:(w+2)]<-c('y','ymin','ymax')
pbilat <- round(100*length(which(yfile$nulatgroup=='B'))/nrow(yfile),0) #% bilat
forplot<-cbind(xfile,yfile[,w:(w+2)])

corspear <-spearman.ci(forplot$x,forplot$y, nrep = 1000, conf.level = 0.95)
rs <- round(corspear$estimate,3)
ci1<-round(corspear$conf.int[1],3)
ci2<-round(corspear$conf.int[2],3)
cortext <- paste0('r[s] = ',rs,'\n[',ci1,', ', ci2,']')

#add some text re % bilateral


myplot <- ggplot(data = forplot,aes(x = x,y = y)) + 
  geom_point(aes(col='black'),size=1.5)+
  geom_errorbar(aes(ymin = ymin,ymax = ymax,col='black')) + 
  geom_errorbarh(aes(xmin = xmin,xmax = xmax,col='black'))+
  geom_hline(yintercept = 0, linetype="solid",col='grey') + 
  geom_vline(xintercept = 0, linetype= "solid", col='grey')  + 
  xlab(methodlabel[meth1])+
  ylab(methodlabel[meth2])+
  xlim(-1,1)+
  ylim(-1,1)+
  ggtitle(mytitle)+
  annotate("text",x = -.5, y = .9, label = cortext,col='black')+
  annotate("text",x = 0.65, y = -.85, label = paste0(pbilat,'% bilateral'),col='black')+
  guides(col=guide_legend(title='Laterality category: fTCD WG'))

allplot[[mycount]] = myplot
}
}

myallplot <- ggarrange(allplot[[1]],allplot[[6]],allplot[[2]],allplot[[7]],allplot[[3]],
                       allplot[[8]],allplot[[4]],allplot[[9]],allplot[[5]],allplot[[10]],nrow=5,ncol=2,common.legend=TRUE)
savename<-paste0('Doppler_fmri2meth_5masks_',mytask,'.jpg')

ggsave(here('Plots',savename),myallplot,width=8,height=15,dpi=300)

#additional plots for powerpoint
myplot1 <- ggarrange(allplot[[1]],allplot[[6]],nrow=1,ncol=2,common.legend=TRUE)
savename<-paste0('Doppler_fmri2meth_MCA_',mytask,'.jpg')

ggsave(here('Plots',savename),myplot1,width=6,height=4,dpi=300)

#additional plots for powerpoint
myplot2 <- ggarrange(allplot[[2]],allplot[[7]],allplot[[3]],allplot[[8]],nrow=2,ncol=2,common.legend=TRUE)
savename<-paste0('Doppler_fmri2meth_fronttemp_',mytask,'.jpg')

ggsave(here('Plots',savename),myplot2,width=6,height=6,dpi=300)

myplot3 <- ggarrange(allplot[[4]],allplot[[9]],allplot[[5]],allplot[[10]],nrow=2,ncol=2,common.legend=TRUE)
savename<-paste0('Doppler_fmri2meth_parcereb_',mytask,'.jpg')

ggsave(here('Plots',savename),myplot3,width=6,height=6,dpi=300)
}


```

