---
title: "LI_toolbox_bootstrap"
author: "Dorothy Bishop"
date: "2023-05-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(here)
require(tidyverse)
require(RNifti) #see https://rdrr.io/cran/RNifti/man/readNifti.html
require(rgl) #3D array plot
require(reshape2)

```

## Background

This is an attempt to implement the LI_boot.m script in R. LI_boot.m is part of LI Toolbox in SPM.


myDir = '/Volumes/Extreme_Pro/_fmri_data/bruckert_raw/FEAT_results/FLIRT_t_outputs/WG1/'
sublist = dir([myDir '*.nii'])  %list dirs with .feat ending
nsub = length(sublist)

%Specify the directory where you want the output .txt file saved
outDir = '/Users/dorothybishop/Rprojects/OptimalLI/bruckert/LIcomparisons/'
%Change the outfile name to anything you like
outfile=fullfile(outDir,'Tbox_WG_MCA2.txt')

%Loop through subjects: could specify desired subset here - currently set
%to run through all files in sublist
for f = 1:nsub
   myfile = fullfile(myDir, sublist(f).name)


```{r setdirs}

dataDir = '/Volumes/Extreme_Pro/_fmri_data/bruckert_raw/FEAT_results/FLIRT_t_outputs/WG1/'
maskfile =   '/Users/dorothybishop/Documents/MATLAB/spm12/toolbox/LI/data/LI-mca2-mask.nii'
exmaskfile =  '/Users/dorothybishop/Documents/MATLAB/spm12/toolbox/LI/data/LI-midline_5_ex.nii'
#for R and L masks I only had .img files, so in matlab used writenifti to convert
Rmaskfile =  '/Users/dorothybishop/Documents/MATLAB/spm12/toolbox/LI/data/Rvol.nii'
Lmaskfile =  '/Users/dorothybishop/Documents/MATLAB/spm12/toolbox/LI/data/Lvol.nii'
filelist = list.files(dataDir)
nsub = length(filelist)
#Specify the directory where you want the output .txt file saved
outDir = '/Users/dorothybishop/Rprojects/OptimalLI/bruckert/R_toolbox_out/'
#Change the outfile name to anything you like
outfile=paste0(outDir,'Tbox_WG_mca2.txt')

```

Now we'll try to read a file and create arrays for data manipulation
This is done by function readcombine

```{r readcombinearrays }
readcombine <- function(myfile,maskfile,exmaskfile,RLfile){
mydata<-readNifti(paste0(dataDir,filelist[f]))
myhead <- niftiHeader(mydata)
mydim <- myhead$dim[2:4]
mydata<-as.matrix(mydata)
dim(mydata)<-mydim #need to explicitly set the dimensions for each array
mymask<-as.matrix(readNifti(maskfile))
dim(mymask)<-mydim
exmask <- as.matrix(readNifti(exmaskfile))
dim(exmask)<-mydim
RLmask <- as.matrix(readNifti(RLfile))
dim(RLmask)<-mydim

returnfile = mydata * mymask * exmask *RLmask
return(returnfile)
}
```

Function for bootstrapped samples


```{r bootstrap}
#Function is done for L and R values from this specific threshold
doboot <- function(vecL,vecR,its){
# generate samples: left...
  bL<-matrix(0,nrow=its)
  bR<-matrix(0,nrow=its)
 
   Lsamples <- as.integer(length(vecL)*perc)
   if (Lsamples>breakpoint){
     Lsamples <- breakpoint #breakpoint is max N samples to take
   }
     Rsamples <- as.integer(length(vecR)*perc)
   if (Rsamples>breakpoint){
     Rsamples <- breakpoint
   }
  jn_li = matrix(NA,nrow=its,ncol=its)
  if((Lsamples>bailout) & (Rsamples>bailout)){ #if sample too small, defaults to jn_li as NA
  for (k in 1:its){                  
   bL[k] <-  sum(sample(vecL, Lsamples, replace = TRUE, prob = NULL)) #sample with replacement
   bR[k] <-  sum(sample(vecR, Rsamples, replace = TRUE, prob = NULL)) #sample with replacement
}

# generate LI-matrix from bootstrapped data: this is done in Toolbox version by pairing each element of  L sample with each element of R sample
# loop over iterations: left first...
# initialise jn_li

  for (k in 1:its){
	l = bL[k]

	# ... then right
	  for (kk in 1:its){
		r = bR[kk]

		# calculate li, store away
		  jn_li[k,kk] = (l-r)/(l+r)
    }
  }
}
return(as.vector(jn_li))
}
```

MAIN LOOP FOR PROCESSING EACH FILE STARTS HERE!

```{r startloop}
# set critical number of voxels (ncr), minimum cluster size (k), and minimum number of voxels (nabort)
  breakpoint = 10000 #default is 10000 - if proportion selected voxels exceeds this, just select this N voxels
  ncr = 10     # default: 10
  k = 5        # default: 5
  bailout = 0   # default: 5 - only compute LI for threshold if N voxels selected by perc is > bailout on either side; else do not compute LI - NB the *plot* from toolbox shows bailout of 0
  
# set iterations and, linked, number of bootstraps at each step
  iter = 20 #default is 20
  its = iter * 5 #default is 5
  perc = 25/100 #proportion to select on each iteration
  
allsum = data.frame(matrix(0,nrow=nsub,ncol=15))
colnames(allsum)<-c('ID','maxthr','voxatmax','meanLI','p5_LImean','p95_LImean','trimmeanLI','p5_trimmeanLI','p95_trimmeanLI','wtmean','p5_wtmean','p95_wtmean','wm','mask','exmask')  
for (f in 1:nsub){
  myfile <- paste0(dataDir,filelist[f])
  print(myfile)
  RLfile <- Lmaskfile
  myarrayL <- readcombine(myfile,maskfile,exmaskfile,RLfile)
   RLfile <- Rmaskfile
  myarrayR <- readcombine(myfile,maskfile,exmaskfile,RLfile)
   mx = max(c(myarrayL,myarrayR))
  #If fixed threshold wanted, need to set mx here
  
  #set thresholds: N thresholds is determined by iter: range by 0 to mx
  thrs <- rep(0, iter)
  voxl = rep(0, iter)
  voxr = rep(0, iter)
  sumLI = data.frame(matrix(0, nrow = iter, ncol = 5))
  colnames(sumLI) <-
    c('threshold', 'NvoxL', 'NvoxR', 'meanLIt', 'trimmeanLIt')
  
  
  jn_all = matrix(nrow = iter, ncol = its ^ 2)
  x = matrix(0, nrow = iter, ncol = its)
  y = matrix(0, nrow = iter, ncol = its)

 
  
 
  for (j in 1:iter){
    thrs[j] <- (j-1)*mx/iter

		    #mask with current threshold
    # threshmask <- myarray
    # threshmask[threshmask<thrs[j]]<-0
    #     threshmask[threshmask>thrs[j]]<-1
    # 
    # con_vol <- 	myarray*threshmask
    # con_vol <- myarray*myarray>thrs[j]
    
 

		  
  #Retain voxels exceeding this threshold in a vector: vector lengths will differ for L and R
  myL <- myarrayL
  myR <- myarrayR
	myL[myL<thrs[j]] <- NA #checked - this works - all values below threshold are now NA
	myR[myR<thrs[j]] <- NA
	
	vecL <- as.vector(myL)
	rmL <- c(which(is.na(vecL)),which(vecL==0))
	vecL <- vecL[-rmL]
	vecR <- as.vector(myR)
	rmR <- c(which(is.na(vecR)),which(vecR==0))
	vecR <- vecR[-rmR]
	Nleft <- length(vecL)
	Nright <- length(vecR)
	voxl[j]<-Nleft
	voxr[j]<-Nright
	jn_all[j,] <- doboot(vecL,vecR,its)
	}



  sumLI$threshold[1:iter] <-thrs
  sumLI$NvoxL[1:iter] <- voxl
  sumLI$NvoxR[1:iter] <- voxr
  sumLI$meanLIt[1:iter] <- rowMeans(jn_all)
  
  for (j in 1:iter){
   sumLI$trimmeanLIt[j] <- mean(jn_all[j,],trim=.25)
  }
   
  #Now do overall stats across all thresholds

  # allsum df to hold overall data for each subject

  maxrow <- max(which(!is.na(sumLI$meanLIt)))
  allsum$ID[f] <- filelist[f]
  allsum$mask[f] <- maskfile
  allsum$exmask[f]<-exmaskfile
   allsum$maxthr[f] <- sumLI$threshold[maxrow] #highest threshold with data
   allsum$voxatmax[f] <- sumLI$NvoxL[maxrow]+sumLI$NvoxR[maxrow]
   allsum$meanLI[f] <- mean(jn_all,na.rm=T)
   allsum$p5_LImean[f] <- quantile(jn_all,.05,na.rm=T)
   allsum$p95_LImean[f] <- quantile(jn_all,.95,na.rm=T)
   
   allsum$trimmeanLI[f] <- mean(jn_all,.25,na.rm=T)
   #For the weighted mean make a new version of jn_all where the number of LIs is proportional to the threshold
   
   jnwt <- jn_all[1:maxrow,]
   wts<-thrs[1:maxrow]/(sum(thrs[1:maxrow]))
   Nwt <- round(wts*dim(jnwt)[1]*dim(jnwt)[2]/2,0) #we'll use all 10K of largest threshold and smaller Ns for lower thresholds
   #initalise jnwt with lowest row, which is row 2 (as zero threshold omitted)
   jnwt<-jn_all[2,1:Nwt[2]]
   for (i in 2:maxrow){
     jnwt <-c(jnwt,jn_all[i,1:Nwt[i]])
   }
   allsum$wtmean[f]<-mean(jnwt)
   allsum$p5_wtmean[f]<-quantile(jnwt,.05)
   allsum$p95_wtmean[f]<-quantile(jnwt,.95)
   top <- min(21,which(sumLI$NvoxL<1),which(sumLI$NvoxR<1))-1 #first row with zero vox on one side - ignore these
   allsum$wm[f] <- sum(sumLI$threshold[1:top]*sumLI$meanLIt[1:top],na.rm=T)/sum(sumLI$threshold[1:top])
}  
  #  par(mfrow=c(2,1))
  # hist(jn_all,breaks=50)
  # hist(jnwt,breaks=50)
write.csv(allsum,here('Toolbox_R','allsumLI_wg_newmca.csv'),row.names=F)
```


```{r tempbit}
#compare old and new mca

allsumnew <- read.csv(here('Toolbox_R','allsumLI_wg_newmca.csv'))
allsumold <- read.csv(here('Toolbox_R','allsumLI_wg_oldmca.csv'))

plot(allsumnew$wtmean,allsumold$wtmean,main='WG_MCA_weightedMean')
abline(a=0,b=1)
abline(h=0,lty='dotted')
abline(v=0,lty='dotted')

plot(allsumnew$trimmeanLI,allsumold$trimmeanLI,main='WG_MCA_trimmedMean')
abline(a=0,b=1)
abline(h=0,lty='dotted')
abline(v=0,lty='dotted')
```
