---
title: "LI_toolbox_bootstrap"
author: "Dorothy Bishop"
date: "2023-05-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(here)
require(tidyverse)
require(RNifti) #see https://rdrr.io/cran/RNifti/man/readNifti.html
require(rgl) #3D array plot
require(reshape2)

```

## Background

This is an attempt to implement the LI_boot.m script in R. LI_boot.m is part of LI Toolbox in SPM.


myDir = '/Volumes/Extreme_Pro/_fmri_data/bruckert_raw/FEAT_results/FLIRT_t_outputs/WG1/'
sublist = dir([myDir '*.nii'])  %list dirs with .feat ending
nsub = length(sublist)

%Specify the directory where you want the output .txt file saved
outDir = '/Users/dorothybishop/Rprojects/OptimalLI/bruckert/LIcomparisons/'
%Change the outfile name to anything you like
outfile=fullfile(outDir,'Tbox_WG_MCA.txt')

%Loop through subjects: could specify desired subset here - currently set
%to run through all files in sublist
for f = 1:nsub
   myfile = fullfile(myDir, sublist(f).name)


```{r setdirs}

dataDir = '/Volumes/Extreme_Pro/_fmri_data/bruckert_raw/FEAT_results/FLIRT_t_outputs/WG1/'
maskfile =   '/Users/dorothybishop/Documents/MATLAB/spm12/toolbox/LI/data/LI-MCA-mask.nii'
exmaskfile =  '/Users/dorothybishop/Documents/MATLAB/spm12/toolbox/LI/data/LI-midline_5_ex.nii'
#for R and L masks I only had .img files, so in matlab used writenifti to convert
Rmaskfile =  '/Users/dorothybishop/Documents/MATLAB/spm12/toolbox/LI/data/Rvol.nii'
Lmaskfile =  '/Users/dorothybishop/Documents/MATLAB/spm12/toolbox/LI/data/Lvol.nii'
filelist = list.files(dataDir)
nsub = length(filelist)
#Specify the directory where you want the output .txt file saved
outDir = '/Users/dorothybishop/Rprojects/OptimalLI/bruckert/R_toolbox_out/'
#Change the outfile name to anything you like
outfile=paste0(outDir,'Tbox_WG_MCA.txt')

```

Now we'll try to read a file and create arrays for data manipulation


```{r readcombinearrays }
readcombine <- function(myfile,maskfile,exmaskfile,RLfile){
mydata<-readNifti(paste0(dataDir,filelist[f]))
myhead <- niftiHeader(mydata)
mydim <- myhead$dim[2:4]
mydata<-as.matrix(mydata)
dim(mydata)<-mydim
mymask<-as.matrix(readNifti(maskfile))
dim(mymask)<-mydim
exmask <- as.matrix(readNifti(exmaskfile))
dim(exmask)<-mydim

sidemask <- as.matrix(readNifti(RLfile))
dim(sidemask)<-mydim

returnfile = mydata * mymask * exmask* sidemask
return(returnfile)
}
```



```{r startloop}
# set iterations and, linked, number of bootstraps at each step
  iter = 4 #default is 20
  its = iter * 5 #default is 5
  perc = 25/100 #proportion to select on each iteration
  
for (f in 1:1){
  myfile <- paste0(dataDir,filelist[f])
  RLfile <- Rmaskfile
  myarrayR <- readcombine(myfile,maskfile,exmaskfile,RLfile)
  RLfile <- Lmaskfile
  myarrayL <- readcombine(myfile,maskfile,exmaskfile,RLfile)
  
  mx = max(myarrayL+myarrayR)
  #If fixed threshold wanted, need to set mx here
  
  #set thresholds: N thresholds is determined by iter: range by 0 to mx
  thrs <- rep(0,iter)
  		voxl = rep(0,iter)
		  voxr = rep(0,iter)
		  jn = matrix(0,nrow=iter,ncol=3)
		  jn_all = matrix(nrow=iter,ncol=its^2)
		  x = matrix(0,nrow=iter,ncol=its)
		  y = matrix(0,nrow=iter,ncol=its)
  for (j in 1:iter){
    thrs[j] <- (j-1)*mx/iter
 #initialise various storage spaces 
		  

		  
  #Retain voxels exceeding this threshold in a vector: vector lengths will differ for L and R
	myarrayL[myarrayL<thrs[j]] <- NA
	myarrayR[myarrayR<thrs[j]] <- NA
	
	vecL <- as.vector(myarrayL)
	rmL <- c(which(is.na(vecL)),which(vecL==0))
	vecL <- vecL[-rmL]
	vecR <- as.vector(myarrayR)
	rmR <- c(which(is.na(vecR)),which(vecR==0))
	vecR <- vecR[-rmR]
	voxl[j]<-length(vecL)
	voxr[j]<-length(vecR)
 }
}
```


