---
title: "R Notebook"
output: html_notebook
---

Image manipulation in R.

This script creates composite figures from .png files created in MRIcroGL.
First chunks do this for L and R images from averaged data from 3 groups; later chunks do similar for the L-R difference files used in mirror method.

To run for main tasks, set do_pp to zero in line 27 and line 147
To run for supplementary (PP tasks) set do_pp to 1.

THIS SCRIPT REQUIRES colscale.png, vertline.png and colscale_yellowgreen.png to be saved in Images folder.

```{r}
require(magick)
require(here)

#myfolder <- here('_optimal_writeup','images','MRIcroGL_maps')

myfolder <- '/Volumes/Extreme_Pro/_fmri_data/bruckert_raw/png_avgs_by_latgroup'



```

Read and crop all files.
```{r cropfiles}
do_pp <-0 #default analysis is 3 main tasks, with do_pp set to 0. Set to 1 to create maps for supplementary material
tasks <- c('WG1','AN5','PP1')
tasknames <- c('Word Generation','Auditory Naming','Semantic Matching')
writefilename <-'bigbrains3gp.tiff'

if (do_pp==1){
tasks <- c('PP1','PP3','PP5')
tasknames <- c('Semantic Match','Perceptual Match','Contrast')
writefilename <-'bigbrainsPP3gp.tiff'
}

groups <- c('lefts','bilats','rights')
sides <- c('L','R')
i = 0
j = 0
images<-list()
imsides<-list()
addback<-c(3,4,9,10,15,16)
for (t in 1:length(tasks)){
  for (g in 1:length(groups)){
    j <-j+1
    for (s in 1:length(sides)){
      i <- i+1
      filename<-paste0(tasks[t],'_',groups[g],sides[s],'.png')
      thisimage <- image_read(paste0(myfolder,'/',filename))
      # if(i %in% addback){
      # thisimage<-image_fill(thisimage, "lightcyan", point = "+100+200", fuzz = 20) #just replaces the colour at that point and other adj points
      # }
    
      images[[i]]<-image_trim(thisimage)
      images[[i]]<-image_scale(images[[i]],200)
    }
    
  }
}

myfolder1 <- here('_optimal_writeup','images')
 colscale <- image_read(paste0(myfolder1,'/colscale.png'))
 colscale <-image_trim(colscale)
 colscale <- image_scale(colscale,200)
 vertline <- image_read(paste0(myfolder1,'/vertline.png'))

```

```{r assemble images}
#Make a big canvas to place images

mycanvas <- image_blank(width = 1250, height = 1000, color = "white")
#first 6 are WG for 3 lat groups, L and R sides
nuimage <- image_composite(mycanvas,images[[1]], offset = "+0+80")
nuimage <- image_composite(nuimage,images[[2]], offset = "+200+80")
nuimage <- image_composite(nuimage,images[[3]], offset = "+400+80")
nuimage <- image_composite(nuimage,images[[4]], offset = "+600+80")
nuimage <- image_composite(nuimage,images[[5]], offset = "+800+80")
nuimage <- image_composite(nuimage,images[[6]], offset = "+1000+80")

#next 6 are AN for 3 lat groups, L and R sides
nuimage <- image_composite(nuimage,images[[7]], offset = "+0+270")
nuimage <- image_composite(nuimage,images[[8]], offset = "+200+270")
nuimage <- image_composite(nuimage,images[[9]], offset = "+400+270")
nuimage <- image_composite(nuimage,images[[10]], offset = "+600+270")
nuimage <- image_composite(nuimage,images[[11]], offset = "+800+270")
nuimage <- image_composite(nuimage,images[[12]], offset = "+1000+270")

#next 6 are PP1 for 3 lat groups, L and R sides
nuimage <- image_composite(nuimage,images[[13]], offset = "+0+460")
nuimage <- image_composite(nuimage,images[[14]], offset = "+200+460")
nuimage <- image_composite(nuimage,images[[15]], offset = "+400+460")
nuimage <- image_composite(nuimage,images[[16]], offset = "+600+460")
nuimage <- image_composite(nuimage,images[[17]], offset = "+800+460")
nuimage <- image_composite(nuimage,images[[18]], offset = "+1000+460")

#add vertical lines
nuimagex <- image_composite(nuimage,vertline,offset="+405,+1")
nuimagex <- image_composite(nuimagex,vertline,offset="+805,+1")

Lstring="N = 16*"
Bstring ="N = 7*"
if(do_pp==1){
 Lstring="N = 16"
 Bstring = "N = 6"
}
nuimage1<-image_annotate(nuimagex, "Left-lateralised", size=25,location="+170+5")
nuimage1<-image_annotate(nuimage1, Lstring, size=18,location="+215+29")
nuimage1<-image_annotate(nuimage1, "Bilateral", size=25,location="+560+5")
nuimage1<-image_annotate(nuimage1, Bstring, size=18,location="+588+29")
nuimage1<-image_annotate(nuimage1, "Right-lateralised", size=25,location="+950+5")
nuimage1<-image_annotate(nuimage1, "N = 9", size=20,location="+1006+29")
nuimage1<-image_annotate(nuimage1, tasknames[1], size=20,location="+15+40")
nuimage1<-image_annotate(nuimage1, tasknames[2], size=20,location="+10+240")
nuimage1<-image_annotate(nuimage1, tasknames[3], size=20,location="+10+430")
nuimage1<-image_annotate(nuimage1, "Left hemisphere", size=20,location="+50+620")
nuimage1<-image_annotate(nuimage1, "Left hemisphere", size=20,location="+450+620")
nuimage1<-image_annotate(nuimage1, "Left hemisphere", size=20,location="+850+620")
nuimage1<-image_annotate(nuimage1, "Right hemisphere", size=20,location="+250+620")
nuimage1<-image_annotate(nuimage1, "Right hemisphere", size=20,location="+650+620")
nuimage1<-image_annotate(nuimage1, "Right hemisphere", size=20,location="+1050+620")



#add scale at bottom
nuimage1<-image_composite(nuimage1,colscale, offset = "+1000+650")
#nuimage1<-image_annotate(nuimage1, "Mean t-statistic:", size=18,location="+860+650")

nuimage1 <-image_crop(nuimage1,"1250x700")

writefolder <- here('_optimal_writeup','images')
image_write(nuimage1,paste0(writefolder,'/',writefilename))
```

 Version for mirror figures


Read and crop all files.
We're using green and yellow version, as it is less confusing, given that the colour contrast now indicates lateralisation rather than activation
```{r cropfilesmirror}
myfolder <- '/Volumes/Extreme_Pro/_fmri_data/bruckert_raw/png_avgs_mirror_by_latgroup'

tasks <- c('WG1','AN5','PP1')
tasknames <- c('Word Generation','Auditory Naming','Semantic Matching')
writefilename <-'mirrorbrains_3gp.tiff'

if (do_pp==1){
tasks <- c('PP1','PP3','PP5')
tasknames <- c('Semantic Match','Perceptual Match','       Contrast')
writefilename <-'mirrorbrainsPP_3gp.tiff'
}


groups <- c('lefts','bilats','rights')

i = 0
j = 0
mimages<-list()

for (t in 1:length(tasks)){
  for (g in 1:length(groups)){
    j <-j+1
      filename<-paste0(tasks[t],'_',groups[g],'.png')
      thisimage <- image_read(paste0(myfolder,'/',filename))
      mimages[[j]]<-image_trim(thisimage)
      mimages[[j]]<-image_scale(mimages[[j]],200)

  }
}

myfolder1 <- here('_optimal_writeup','images')
#colscale was created in powerpoint
 colscalem <- image_read(paste0(myfolder1,'/colscale_yellowgreen.png'))
 colscalem <-image_trim(colscalem)
 colscalem <- image_scale(colscalem,230)


```

```{r assemblemirrorimages}
#Make a big canvas to place images

mycanvas <- image_blank(width = 800, height = 1000, color = "white")
#first 3 are WG for left, bilat and right lateralised, L and R sides


#offsets are distances for horiz and vertical
nuimage <- image_composite(mycanvas,mimages[[1]], offset = "+0+80")
nuimage <- image_composite(nuimage,mimages[[2]], offset = "+200+80")
nuimage <- image_composite(nuimage,mimages[[3]], offset = "+400+80")

#next 3 are AN for  left, bilat and right lateralised, L and R sides
nuimage <- image_composite(nuimage,mimages[[4]], offset = "+0+270")
nuimage <- image_composite(nuimage,mimages[[5]], offset = "+200+270")
nuimage <- image_composite(nuimage,mimages[[6]], offset = "+400+270")

#next 3 are PP1 for left, bilat and right lateralised, L and R sides
nuimage <- image_composite(nuimage,mimages[[7]], offset = "+0+460")
nuimage <- image_composite(nuimage,mimages[[8]], offset = "+200+460")
nuimage <- image_composite(nuimage,mimages[[9]], offset = "+400+460")

Lstring="N = 16*"
Bstring ="N = 7*"
if(do_pp==1){
 Lstring="N = 16"
 Bstring = "N = 6"
}

nuimage1<-image_annotate(nuimage, "Left-lateralised", size=25,location="+30+5")
nuimage1<-image_annotate(nuimage1, Lstring, size=18,location="+80+29")
nuimage1<-image_annotate(nuimage1, "Bilateral", size=25,location="+270+5")
nuimage1<-image_annotate(nuimage1, Bstring, size=18,location="+286+29")
nuimage1<-image_annotate(nuimage1, "Right-lateralised", size=25,location="+410+5")
nuimage1<-image_annotate(nuimage1, "N = 9", size=18,location="+480+29")
nuimage1<-image_annotate(nuimage1, tasknames[1], size=20,location="+250+50")
nuimage1<-image_annotate(nuimage1, tasknames[2], size=20,location="+250+240")
nuimage1<-image_annotate(nuimage1, tasknames[3], size=20,location="+250+430")


#add scale at bottom
nuimage1<-image_composite(nuimage1,colscalem, offset = "+360+620")
#nuimage1<-image_annotate(nuimage1, "Mean t-statistic L-R difference:", size=18,location="+100+620")

nuimage1 <-image_crop(nuimage1,"600x670")

writefolder <- here('_optimal_writeup','images')
image_write(nuimage1,paste0(writefolder,'/',writefilename))
```

Redo for powerpoint slides.  Each task separate; 3 subgroups in rows. Include both regular and mirror (now termed mimage)

First make codes to keep track of which is which
```{r makecodes}
mynum <- 0
dfcode <-data.frame(matrix(NA,nrow=18,ncol=4))
for (t in tasks){
  for (g in groups){
    for (s in sides){
      mynum<-mynum+1
      dfcode[mynum,1]<-mynum
      dfcode[mynum,2]<-t
      dfcode[mynum,3]<-g
      dfcode[mynum,4]<-s
    }
  }
}

mynum <- 0
dfmcode <-data.frame(matrix(NA,nrow=9,ncol=3))
for (t in tasks){
  for (g in groups){
      mynum<-mynum+1
      dfmcode[mynum,1]<-mynum
      dfmcode[mynum,2]<-t
      dfmcode[mynum,3]<-g
    
  }
}

```

```{r assemblemirrorimagesbytask}
#Make a big canvas to place images
for (t in 1:3){
  writefilename <- paste0('brains_',tasks[t],'.png')
mycanvas <- image_blank(width = 800, height = 1000, color = "white")

basenum1 <- 6*(t-1)
basenum2 <- 3*(t-1)

#offsets are distances for horiz and vertical - start with L hem 3 gps
nuimage <- image_composite(mycanvas,images[[(basenum1+1)]], offset = "+50+50")
nuimage <- image_composite(nuimage,images[[(basenum1+3)]], offset = "+50+270")
nuimage <- image_composite(nuimage,images[[(basenum1+5)]], offset = "+50+490")

#next R hem 3 gps
nuimage <- image_composite(nuimage,images[[(basenum1+2)]], offset = "+250+50")
nuimage <- image_composite(nuimage,images[[(basenum1+4)]], offset = "+250+270")
nuimage <- image_composite(nuimage,images[[(basenum1+6)]], offset = "+250+490")

#next 3 are mirror diffs for 3 gps
nuimage <- image_composite(nuimage,mimages[[(basenum2+1)]], offset = "+550+50")
nuimage <- image_composite(nuimage,mimages[[(basenum2+2)]], offset = "+550+270")
nuimage <- image_composite(nuimage,mimages[[(basenum2+3)]], offset = "+550+490")

Lstring="N = 16*"
Bstring ="N = 7*"
if(do_pp==1){
 Lstring="N = 16"
 Bstring = "N = 6"
}

nuimage1<-image_annotate(nuimage, "Left-lateralised", size=25,location="+30+0")
nuimage1<-image_annotate(nuimage1, Lstring, size=18,location="+30+25")
nuimage1<-image_annotate(nuimage1, "Bilateral", size=25,location="+30+220")
nuimage1<-image_annotate(nuimage1, Bstring, size=18,location="+30+245")
nuimage1<-image_annotate(nuimage1, "Right-lateralised", size=25,location="+30+465")
nuimage1<-image_annotate(nuimage1, "N = 9", size=18,location="+30+490")

nuimage1<-image_annotate(nuimage1, "Left hem", size=20,location="+100+650")
nuimage1<-image_annotate(nuimage1, "Right hem", size=20,location="+300+650")
nuimage1<-image_annotate(nuimage1, "L-R", size=20,location="+650+650")


#add scale at bottom
nuimage1<-image_composite(nuimage1,colscale, offset = "+100+700")
nuimage1<-image_composite(nuimage1,colscalem, offset = "+500+700")


#nuimage1<-image_annotate(nuimage1, "Mean t-statistic L-R difference:", size=18,location="+100+620")

nuimage1 <-image_crop(nuimage1,"800x750")

writefolder <- here('_optimal_writeup','images')
image_write(nuimage1,paste0(writefolder,'/',writefilename))
}
```


